Modular analysis of gene expression data with R

### 2010-01-11 isanote/modular.tex
Final version of the ISA application note.

In this short note, we introduce two BioConductor \citep{BioC}, software
packages written in GNU~R: The~\Rpackage{isa2} includes a highly optimized
implementation of the ISA and~\Rpackage{eisa} provides a convenient interface
to run the ISA, visualize its output and puts the biclusters into
biological context.

>>>>

In this short note, we introduce two BioConductor \citep{BioC}, software
packages written in GNU~R: The~\Rpackage{isa2} package includes a highly optimized
implementation of the ISA and the~\Rpackage{eisa} package provides a convenient interface
to run the ISA, visualize its output and put the biclusters into
biological context.
